Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-02 paper.tex
Write down the steps of the scheme

@@

>>>>

And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.

@@

Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation....

\section{Conclusion}

This is a placeholder. Lorem ipsum...
